---
title: "Who's using Statistics Denmark administrative register data?"
author: "Andreas Tyge Møller"
date: "28 okt 2018"
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Who's using administrative register data from Statistics Denmark ?

Statistics Denmark publishes annual lists of all active projects using their
administrative register data, along with information on who's responsible for 
the project, the project title, and a few other things. The information is 
available here: 
<https://www.dst.dk/da/TilSalg/Forskningsservice/Registerforskning/projekter>

The tables as somewhat messy html documents generated by SAS, but I just want a 
simple overview of who the most frequent users of the data are.

## Getting and structuring the data
Data is available for the years 2010-2017
```{r}
years_w_data <- c(2010:2017)
```

Getting and structuring the data isn't all that interesting so I wrote a
function to take care of this bit.
```{r, message=FALSE}
library(XML)
source("get_data.R")
data <- lapply(years_w_data, FUN=get_data)
data_all <- do.call("rbind", data)
```
```{r include=FALSE}
data_all$Organization <-
  gsub("258. DAMVAD",
       "445. DAMVAD Analytics", data_all$Organization)
data_all$Organization <-
  gsub("62. Rockwool Fondens Forskningsenhed",
       "62. Rockwool Fonden", data_all$Organization)
```

The data contains all active projects each year. However, I am mostly interested
in the number of distinct projects for each organization so for multi-year
projects, I'm only interested in the first time the project appears in the list.
```{r, message=FALSE}
library(dplyr)
distinct_projects <- data_all %>% 
  group_by(Project_number) %>% 
  filter(Year==min(Year))
```

So which private company has had most projects the past three years?
```{r include=FALSE}
private_companies <- c("445. DAMVAD Analytics",
                       "53. COWI A/S, Division 1",
                       "48. Epinion A/S",
                       "44. PLS RAMBØLL Management A/S",
                       "329. Incentive",
                       "162. Teknologisk Institut – Center for Analyse og Erhvervsfremme",
                       "318. Mploy A/S",
                       "224. Deloitte Consulting, Deloitte, Statsautoriseret Revisionspartnerselskab",
                       "480. Højbjerre Brauer Schultz",
                       "72. Copenhagen Economics",
                       "387. Moos-Bjerre & Lange ApS",
                       "243. Oxford Research A/S",
                       "293. McKinsey & Company",
                       "411. BDO Consulting",
                       "481. IRIS Group",
                       "488. Analyse & Tal",
                       "461. Marselisborg")
distinct_projects <- distinct_projects %>% 
  mutate(private = ifelse(Organization %in% private_companies, 1, 0))
```
```{r}
most_projects <- distinct_projects %>% 
  filter(Year>=2015) %>%
  filter(Organization %in% private_companies) %>% 
  group_by(Organization) %>% 
  summarise(Projects = n()) %>% 
  arrange(desc(Projects))
knitr::kable(most_projects)
```
```{r, message=FALSE}
library(ggplot2)
projects_plot <- ggplot(data = most_projects,
       aes(x = reorder(Organization, Projects), y = Projects, fill="#97d8f2")) +
  geom_col() +
  scale_fill_manual(values ="#97d8f2") +
  labs(x="", title = "DAMVAD Analytics started more projects than any other private company in the past three years") +
  coord_flip() +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.9)) +
  theme(legend.position = "none")
```
```{r echo=FALSE}
print(projects_plot)
```

So DAMVAD Analytics is the private company that has used the data the most. But
how has their usage varied over the years?
```{r}
DAMVAD_Analytics <- distinct_projects %>% 
  filter(Organization == "445. DAMVAD Analytics") %>% 
  group_by(Year) %>% 
  summarise(Projects = n())
plot(ggplot(data = DAMVAD_Analytics,
       aes(x = Year, y = Projects, fill="#97d8f2")) +
  geom_col() +
  scale_fill_manual(values ="#97d8f2") +
  labs(x="", title = "DAMVAD Analytics typically has 10-15 projects every year") +
  theme_minimal() +
  theme(legend.position = "none"))
```
